On Devon Allen's Disqualification at the 2022 Track and Field World Championship

### 2023-04-25 Manuscript/manuscript.tex
Updates for tuesday meeting

\begin{table}
\begin{center}
  \caption{Rection times for four United States Athletes at the 2022 USA Track
  and Field World Championships and the 2022 World Track and Field Championship.
  ``N/A" was used for any athlete that did not compete and thus did not register 
  a reaction time.}
  \begin{tabular}{c c c c c c c} 
   \toprule
   Athlete & USA H & USA S & USA F & World H & World S & World F \\ [0.5ex] 
   \midrule
   Devon Allen & 0.201 & 0.153 & 0.160 & 0.123 & 0.101 & 0.099 \\ 
   Trey Cunningham & 0.186 & 0.185 & 0.182 & 0.115 & 0.120 & 0.109 \\
   Grant Holloway & 0.192 & 0.190 & N/A & 0.147 & 0.128 & 0.124 \\
   Daniel Roberts & 0.181 & 0.200 & 0.183 & 0.179 & N/A & N/A \\ [0.5ex]
   \bottomrule
  \end{tabular}
  \label{fig:USAvsWorld}

@@

\jy{You have two such datasets in the analysis. Use one paragraph for each.}
\of{Split it into 2 sections, do you stil want me to do something else?}

@@

To better understand this model, we can identify the gamma model in terms of the
commonly used shape and scale parameters. For a gamma distribution with
shape~$a$ and scale~$b$, we have mean $\mu = ab$ and variance $v = ab^2$. The
variance as a function of the mean $\mu$ in the GLM sense is
$v(\mu) = \mu^2 / a$, which implies that the dispersion parameter
$\phi = 1 / a$. Therefore, for the gamma mixed-effect model, the conditional
gamma distribution of the reaction time $Y_{ij}$ given the venue effect $z_i$
has shape $a = 1 / \phi$ and scale $b = g^{-1}(\alpha + z_i) \phi$. The marginal
distribution of $Y_{ij}$ is a scale-mixture of gamma distributions, which can be
easily simulated from once the parameters are estimated. A large number of
random numbers generated from the fitted mixture distribution can be used to
approimate the probability of observing a reaction time faster than any given
threshold.  We want the probability of a reaction time being less than 0.1
seconds in order to gauge if that is a reasonable disqualification barrier.

>>>>

\begin{table}
\begin{center}
  \caption{Reaction times for four United States Athletes at the 2022 USA Track
  and Field World Championships and the 2022 World Track and Field Championship.
  ``N/A" was used for any athlete that did not compete and thus did not register 
  a reaction time.}
  \begin{tabular}{c c c c c c c} 
   \toprule
   Athlete & USA H & USA S & USA F & World H & World S & World F \\ [0.5ex] 
   \midrule
   Devon Allen & 0.201 & 0.153 & 0.160 & 0.123 & 0.101 & 0.099 \\ 
   Trey Cunningham & 0.186 & 0.185 & 0.182 & 0.115 & 0.120 & 0.109 \\
   Grant Holloway & 0.192 & 0.190 & N/A & 0.147 & 0.128 & 0.124 \\
   Daniel Roberts & 0.181 & 0.200 & 0.183 & 0.179 & N/A & N/A \\ [0.5ex]
   \bottomrule
  \end{tabular}
  \label{fig:USAvsWorld}

@@

\jy{You have two such datasets in the analysis. Use one paragraph for each.}
\of{Split it into 2 sections, do you still want me to do something else?}

@@

To better understand this model, we can identify the gamma model in terms of the
commonly used shape and scale parameters. For a gamma distribution with
shape~$a$ and scale~$b$, we have mean $\mu = ab$ and variance $v = ab^2$. The
variance as a function of the mean $\mu$ in the GLM sense is
$v(\mu) = \mu^2 / a$, which implies that the dispersion parameter
$\phi = 1 / a$. Therefore, for the gamma mixed-effect model, the conditional
gamma distribution of the reaction time $Y_{ij}$ given the venue effect $z_i$
has shape $a = 1 / \phi$ and scale $b = g^{-1}(\alpha + z_i) \phi$. The marginal
distribution of $Y_{ij}$ is a scale-mixture of gamma distributions, which can be
easily simulated from once the parameters are estimated. A large number of
random numbers generated from the fitted mixture distribution can be used to
approximate the probability of observing a reaction time faster than any given
threshold.  We want the probability of a reaction time being less than 0.1
seconds in order to gauge if that is a reasonable disqualification barrier.
